---
title: "Crime in Adelaide"
author: "Jubin Katyal"
date: "November 9, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r library,echo = FALSE}
library(prfajkatyal)

```
## Aim 

The aim of this report is to study the trends associated with frequency of criminal-offence incidients that fall under "Level - 1" category. We will focus on monthly trends related to "SERIOUS CRIMINAL TRESPASS" incidents for areas with postcodes: 5010 and 5013, and base our insights after studying such trends observed from 2012 to 2017.

## Results

#### Summarized Data

```{r,echo = FALSE}

```

#### Relevant Plots

```{r,echo = FALSE}
library(ggplot2)
library(readxl)
library(data.table)
postcodes_vec <- c("5010","5013")
offence <- "SERIOUS CRIMINAL TRESPASS"
stat_2012_2013 = setDT(read_excel("data/crime-statistics-2012-13.xlsx"))
setnames(stat_2012_2013, c("date", "suburb", "postcode", "offence_level_1",
                    "offence_level_2", "offence_level_3", "offence_count"))
stat_2013_2014 <- setDT(read_excel("data/crime-statistics-2013-14.xlsx"))
setnames(stat_2013_2014, c("date", "suburb", "postcode", "offence_level_1",
                    "offence_level_2", "offence_level_3", "offence_count"))
stat_2014_2015 <- setDT(read_excel("data/crime-statistics-2014-15.xlsx"))
setnames(stat_2014_2015, c("date", "suburb", "postcode", "offence_level_1",
                    "offence_level_2", "offence_level_3", "offence_count"))
stat_2015_2016 <- setDT(read_excel("data/crime-statistics-2015-16.xlsx"))
setnames(stat_2015_2016, c("date", "suburb", "postcode", "offence_level_1",
                    "offence_level_2", "offence_level_3", "offence_count"))
stat_2016_2017 <- setDT(read_excel("data/crime-statistics-2016-17.xlsx"))
setnames(stat_2016_2017, c("date", "suburb", "postcode", "offence_level_1",
                    "offence_level_2", "offence_level_3", "offence_count"))
graph_1 <- offence_trends(stat_2012_2013, offence, postcodes_vec)
graph_1
graph_2 <- offence_trends(stat_2013_2014, offence, postcodes_vec)
graph_2
graph_3 <- offence_trends(stat_2014_2015, offence, postcodes_vec)

graph_4 <- offence_trends(stat_2015_2016, offence, postcodes_vec)

graph_5 <- offence_trends(stat_2016_2017, offence, postcodes_vec)

c_plot <- cowplot::plot_grid(graph_1,graph_2,graph_3,graph_4,graph_5)

plot(c_plot)
```

## Observations

After careful observation of the above data, it can be stated that for some months, such as 
